
\documentclass[]{vansh-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Vansh}{Bajaj}{ \urlstyle{same}\url{https://vanshbajaj.me} \\
\href{mailto:vansh2795@gmail.com}{vansh2795@gmail.com} | 562.284.9593
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{California State University, Long Beach}
\descript{MS in Computer Science}
\location{Graduated May 2019 | Long Beach,CA \\ Cum. GPA: 3.1}
\sectionsep

\subsection{Uttar Pradesh Technical University}
\descript{B.Tech in Information Technology}
\location{Graduated June 2017 | Uttar Pradesh,India}
\sectionsep

\subsection{Montfort School}
\location{Graduated. May 2013|  New Delhi, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/vansh2795}{\custombold{vansh2795}} \\
LinkedIn://  \href{https://www.linkedin.com/in/vansh-bajaj-33a76a146/}{\custombold{vansh-bajaj}} \\
Hackerrank://  \href{https://www.hackerrank.com/vansh2795}{\custombold{vansh2795}} \\
DataCamp://  \href{datacamp.com/profile/vanshbajaj}{\custombold{vanshbajaj}} \\
Facebook://  \href{https://www.facebook.com/vansh.bajaj.58}{\custombold{vansh.bajaj}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Good:}
{\custombold
{Python}} \textbullet{}  {\custombold{HTML5}} \textbullet{} {\custombold{CSS3}} \textbullet{} {\custombold{JavaScript}} 
{\custombold{DOM}} \textbullet{} {\custombold{Windows}}  \\
\location{Average:}
 {\custombold{C++}} \textbullet{} {\custombold{Java}} \textbullet{} {\custombold{Django}} \textbullet{} \LaTeX\ \textbullet{} {\custombold{Solidity}} \textbullet{} {\custombold{MySQL}} \textbullet{} {\custombold{Linux}} \textbullet{}{\custombold{Git}} \\
\location{Familiar:}
{\custombold{C\#}} \textbullet{} {\custombold{ jQuery}} \textbullet{} {\custombold{ Android}}  \textbullet{} {\custombold{ Dart}} \textbullet{} {\custombold{Flutter}} 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Advanced Topics in Programming Languages\\
Advanced Operating Systems \\
Advanced Software Engineering  \\
Object Oriented Analysis \& Design \\
Advanced Analysis of Algorithms \\
Requirements Engineering \\
Hardware Software Co-Design \\
Artificial Intelligence \\
Memory Design Implementation \\
Deep Learning \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{INDI Foundation}
\descript{| Lead Operations Engineer | Mostly Remote}
\location{July 2017 – August 2018 | Knowledge Park V-Noida, Uttar Pradesh, India.}
\vspace{\topsep} 
\begin{tightemize}
\item  Creation and Development of INDI Smart Contract. Managing the development of website – \href{https://indi.live/}{\custombold{ https://indi.live/}}. Conducted research, coordinated team and collaborated on the development of whitepaper. Responsible for the managing teams of interns.
\item  {\custombold{Stack - Intelij IDEA, Solidity, Ethereum Blockchain, HTML, CSS, JavaScript, PHP, LaTeX.}}
\end{tightemize}
\sectionsep

\runsubsection{Johnson Controls}
\descript{|Information Technology Intern }
\location{ June 2016 – July 2016 | Pune, Maharashtra , India}
\begin{tightemize}
\item Worked with the IT department to effectively analyze and solve technical issues.Developed a content management system.Conducted research, compiled data and prepared requirements for an office wide portal.
\item {\custombold{ Stack - Eclipse, HTML, CSS, JavaScript, Struts, JSP, Hibernate, Apache Tomcat.}}\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
\runsubsection{Predicting hand drawn sketches using Google’s QuickDraw dataset in real time }
\smallskip
\begin{tightemize}
\item Used Convolutional Neural Network to classify and predict data.
\item {\custombold{Stack - Spyder, Python, OpenCV-Python, Keras, Pandas, h5py, Scipy, Scikit-learn}}
\end{tightemize}
\sectionsep

\runsubsection{Real Time Audio Filter}
\smallskip
\begin{tightemize}
\item {\custombold{Stack - Vivado Design Suite, Zybo Zynq-7000 ARM/FPGA SoC board ,Xilinx SDK ,C\#.}}
\end{tightemize}
\sectionsep

\runsubsection{Simulation Based comparative study of open source memory simulators that model DRAM and NVM’s }
\smallskip
\begin{tightemize}
\item Results compared on metrics such as – Simulated Clock Cycles, Throughput, Memory Consumption and Average Power Consumption.
\item {\custombold{ Stack - Ubuntu 18.04.2, Gem5, NVMain, Ramulator, DRAMSim2, LaTeX.}}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}
\medskip
\begin{tightemize}
\item DataCamp - \href{https://www.datacamp.com/statement-of-accomplishment/track/18edab84e8804850e65a90a1caf050071bdf14cd}{\custombold{Data Scientist}} with Python.	
\end{tightemize}
\begin{tightemize}
\item DataCamp - \href{https://www.datacamp.com/statement-of-accomplishment/track/95f7129f30a36a11b3c1e91796e10069fa2205a4}{\custombold{Data Analyst}}  with Python.	
\end{tightemize}
\begin{tightemize}
\item Udemy - \href{https://www.udemy.com/certificate/UC-V5V2TIG4/}{\custombold{Ethereum \& Solidity:}}  The Complete Developers Guide. 	
\end{tightemize}
\begin{tightemize}
\item Udemy -  \href{https://www.udemy.com/certificate/UC-5ZX7ROX0/}{\custombold{Python \& Django}} Web Developer’s Guide.	
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\medskip
\begin{tightemize}
\item Cryptocurrency Trading, Basketball, Cricket, Working out, History, Politics, Reading. 
\end{tightemize}
\sectionsep
\end{minipage} 
\end{document}